\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-09 k-planar.tex

For any integer $d\ge 3$, an embedded (multi)graph $G$ is \defin{$d$-framed} if it has a biconnected plane spanning (multi)subgraph $G_0$, whose facial cycles each have length at most $d$,  and such that the interior of each edge in $E(G)\setminus E(G_0)$ is contained in some face of $G_0$. The embedded (multi)graph $G_0$ is called the \defin{frame} of $G$. This definition (for simple graphs) was introduced by \citet{BDGGMR}.  A $d$-framed graph $G$ is \defin{edge-maximal} with respect to its frame $G_0$ if, for each face $F$ of $G_0$ and each pair of distinct vertices $v,w\in V(F)$, $vw\in E(F)$ or $G$ contains an edge $vw$ whose interior is contained in $F$.

\note{DW}{The word ``interior'' may be misinterpreted when refering to the outerface (see referee's comment). Shall we just write ``contained in some face''? Do we need to change this elsewhere?}
\note{PM}{Done.  I've changed occurrences elsewhere also.  Under our definitions (in Section 2.3) the faces of $G$ are open sets so in $F$ already means in the interior of $F$.  In one instance, I changed ``in the interior or boundary of $F$'' to ``in the closure of $F$.''}

>>>>

For any integer $d\ge 3$, an embedded (multi)graph $G$ is \defin{$d$-framed} if it has a biconnected plane spanning (multi)subgraph $G_0$, whose facial cycles each have length at most $d$,  and such that the interior of each edge in $E(G)\setminus E(G_0)$ is contained in some face (possibly the outer face) of $G_0$. The embedded (multi)graph $G_0$ is called the \defin{frame} of $G$. This definition (for simple graphs) was introduced by \citet{BDGGMR}.  A $d$-framed graph $G$ is \defin{edge-maximal} with respect to its frame $G_0$ if, for each face $F$ of $G_0$ and each pair of distinct vertices $v,w\in V(F)$, $vw\in E(F)$ or $G$ contains an edge $vw$ whose interior is contained in $F$.

\note{DW}{The word ``interior'' may be misinterpreted when refering to the outerface (see referee's comment). Shall we just write ``contained in some face''? Do we need to change this elsewhere?}
\note{PM}{Done.  I've changed occurrences elsewhere also.  Under our definitions (in Section 2.3) the faces of $G$ are open sets so ``in $F$'' already means ``in the interior of $F$.''}
